The Astropy Project

### 2017-10-20 main.tex
Update on Overleaf.

\subsection{Coordination of Astropy}
% Kelle

@@

\subsection{Astropy development model, astropy ecosystem}
% Erik
This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.

\subsection{Concept of affiliated packages}
% it may be described in previous subsection, if not the Brigitta can try to
% write it up
%
\par A major part of the \astropy~project is the concept of
``Affiliated Packages''. An affiliated package is an astronomy-related
\python~package that is not part of the \astropypkg~core package, but
has requested to be included as part of the \astropy project's
community. These packages support the goals and vision of \astropy~of
improving code reuse, interoperability, and embracing good coding
practices such as testing and thorough documentation. \astropypkg{}
version 2.0 supports \python~2.7 and \python~3.4+, affiliated packages
are strongly encouraged to support at least \python~3.x.
%
\par Affiliated packages contain functionality that is more specialized, or
have license incompatibility, or have enough external dependencies (e.g. GUI
libraries) that limit their integration possibility into the core and thus
they are more suitable to be separate packages. Starting as an affiliate 
package is also seen as a good strategy for functionality that is aimed for
the \astropypkg~core but is currently undergo rapid development and can 
benefit from a different release cycle while stabilizing its API. 
%
\par In general we hope that becoming an affiliated package is seen as 
a good way for new and existing packages to gain exposure.
%
\inlinecomment{BMS}{TODO: write about the process of becoming affiliated, and project packages}
%
\subsection{Mixin}

\subsection{Accuracy testing across many different implementation}

@@

% \subsection{Analytic Functions}
% moved to models and depreciated --
% just here for completeness at the moment
\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
\subsection{Units and quantities}
\label{sec:units}
% Marten, Adrian

@@

\subsection{Constants}
% David S.
versioning

@@

@@

\subsubsection{NDDdata}
% Matt C., Michael, or Steve C.
% Larry (nddata.utils)
%NOTE (Larry), The package is nddata, which includes the NDData object.  %Don't forget the nddata.utils functionality (e.g. Cutout2D, block\_reduce, %etc.).

\subsubsection{Tables}
\label{sec:table}
% Tom A.
QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3

@@

% Tom R. will work on this on Oct 18 and/or 19.

@@

\subsubsection{Creating color RGB images}
% include images

Lupton et al. (2004) describe an “optimal” algorithm for producing red-green- blue composite images from three separate high-dynamic range arrays. The \package{visualization} package provies a convenience function to create such an image.  It also includes an associated set of classes to provide alternate scalings.  The SDSS SkyServer color images were made using a variation on this technique.

\subsection{Utils}
% Lim

@@

%
\subsubsection{Robust Statistical Estimators}
\inlinecomment{BMS}{Can we highlight in a sentence for each of the ones below how they are different from e.g. the scipy equivalents?}

@@

{\bf Sigma Clipping:}
Sigma clipping provides a fast method to identify outliers in a distribution. For a distribution of points, a center and a standard deviation are calculated. Values which are a set number of sigma times the standard deviation away from the center are rejected. The process can be iterated to further reject outliers.

{\bf Median Absolute Deviation:}
The median absolute deviation (MAD) is a measure of the spread of a distribution and is defined as median(abs(a - median(a))). For a normal distribution, the MAD is related to the standard deviation by a factor of 1.4826, and a convenience function is available to apply the conversion.

{\bf Biweight Estimators: }
A set of functions are included in the \package{stats} package that use the biweight formalism. These functions have long been used in astronomy, particularly to calculate the velocity dispersion of galaxy clusters [XXX].

@@

\inlinecomment{BMS}{What about pytest-astropy, should we inlude it here, or
  for the future section?}
% \section{State of the Ecosystem}
% Commenting out unless a clear statement is added

\section{Learning Astropy}
\label{sec:learning}
% Kelle, Adrian
\inlinecomment{BMS}{would astropy learn mature enough to described in the paper, or maybe it should go as a subsection for the next, future of astropy section?}

Explain components: Documentation, Tutorials, and lessons

@@

dropping \python 2 support, growths of affiliated packages
Summary

\acknowledgments

@@

\software{\package{astropy} (\citealt{astropy}),
          \package{numpy} (\citealt{numpy}),
          \package{scipy} (\url{https://www.scipy.org/}),
          \package{matplotlib} (\url{https://matplotlib.org/}),
          }

@@

>>>>

\subsection{Coordination of Astropy}
\inlinecomment{Kelle}

@@

\subsection{Astropy development model, astropy ecosystem}
\inlinecomment{Needs writing by EJT}

This subsection should include some basic statistics about the contributors, commits, line of code etc. up to the 2.0 release when we know it.

\subsection{Concept of affiliated packages}
% it may be described in previous subsection, if not the Brigitta can try to
% write it up
%
\par A major part of the \astropy~project is the concept of
``Affiliated Packages''. An affiliated package is an astronomy-related
\python~package that is not part of the \astropypkg~core package, but
has requested to be included as part of the \astropy project's
community. These packages support the goals and vision of \astropy~of
improving code reuse, interoperability, and embracing good coding
practices such as testing and thorough documentation. \astropypkg{}
version 2.0 supports \python~2.7 and \python~3.4+, affiliated packages
are strongly encouraged to support at least \python~3.x.
%
\par Affiliated packages contain functionality that is more specialized, or
have license incompatibility, or have enough external dependencies (e.g. GUI
libraries) that limit their integration possibility into the core and thus
they are more suitable to be separate packages. Starting as an affiliate 
package is also seen as a good strategy for functionality that is aimed for
the \astropypkg~core but is currently undergo rapid development and can 
benefit from a different release cycle while stabilizing its API. 
%
\par In general we hope that becoming an affiliated package is seen as 
a good way for new and existing packages to gain exposure.
%
\inlinecomment{BMS}{TODO: write about the process of becoming affiliated, and project packages into the future section below}
%
%\subsection{Mixin}

%\subsection{Accuracy testing across many different implementation}

@@

% \subsection{Analytic Functions}
% moved to models and depreciated --
% just here for completeness at the moment
\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
\subsection{Units and quantities}
\label{sec:units}
\inlinecomment{Marten, Adrian}{}

@@

\subsection{Constants}

\inlinecomment{David S.}

versioning

@@

\inlinecomment{Tom, Marten?}

@@

\subsubsection{nddata}

\inlinecomment{Matt C., Steve C.?}

NDData object:

%Larry:  Don't forget the nddata.utils functionality (e.g. Cutout2D, block\_reduce, %etc.).

\subsubsection{Tables}
\label{sec:table}

\inlinecomment{Tom A.}

QTable is new, mixin columns for time and coordinates. Table operations were added in v0.3

@@

One of the most common tasks by astronomers dealing with observational data is to make figures with images that include the correct coordinates (formatted e.g. as sexagesimal values) and optiona
The \package{visualization} package
% Tom R. will work on this on Oct 18 and/or 19.

@@

\subsubsection{Creating color RGB images}
\citep{Lupton2004} describe an “optimal” algorithm for producing red-green- blue composite images from three separate high-dynamic range arrays. The \package{visualization} package provies a convenience function to create such an image.  It also includes an associated set of classes to provide alternate scalings.  The SDSS SkyServer color images were made using a variation on this technique.
% mention LSST contribution (Zenodo ref?)
% include images here

%\subsection{Utils}
% Lim

@@

%
\subsubsection{Robust Statistical Estimators}
\inlinecomment{BMS}{Can we highlight in a sentence for each of the ones below how they are different from e.g. the scipy equivalents?}
\inlinecomment{LDB}{Thanks.  I did this for sigma clipping.  Scipy doesn't have functions for the others...}

@@

{\bf Sigma Clipping:}
Sigma clipping provides a fast method to identify outliers in a distribution. For a distribution of points, a center and a standard deviation are calculated. Values which are a set number of sigma times the standard deviation away from the center are rejected. The process can be iterated to further reject outliers.  It should be noted that the \package{scipy} sigma clipping function provides a subset of functionality of the \package{astropy.stats} function.  The \package{astropy.stats} version can take a masked array as input and it allows the user to specify the number of iterations, the data axis on which to perform the clipping, and the functions used to calculate the center and standard deviation in the data.

{\bf Median Absolute Deviation:}
The median absolute deviation (MAD) is a measure of the spread of a distribution and is defined as median(abs(a - median(a))). For a normal distribution, the MAD is related to the standard deviation by a factor of 1.4826 (the normal inverse cumulative distribution function evaluated at probabilty $P=3/4$), and a convenience function is available to apply the conversion.

{\bf Biweight Estimators: }
A set of functions are included in the \package{stats} package that use the biweight formalism. These functions have long been used in astronomy, particularly to calculate the velocity dispersion of galaxy clusters \citep{Beers1990}.

@@

\inlinecomment{BMS}{What about pytest-astropy, should we inlude it here, or
  for the future section?}
\inlinecomment{PLL}{pytest-astropy is v3, right?}
% \section{State of the Ecosystem}
% Commenting out unless a clear statement is added

%\section{Learning Astropy}
%\label{sec:learning}
% Kelle, Adrian
%\inlinecomment{BMS}{would astropy learn mature enough to described in the paper, or maybe it should go as a subsection for the next, future of astropy section?}

%Explain components: Documentation, Tutorials, and lessons

@@

dropping \python 2 support, growths of affiliated packages
Summary
learning astropy 
\acknowledgments

@@

\software{\package{astropy} (\citealt{astropy}),
          \package{numpy} (\citealt{numpy}),
          \package{scipy} (\url{https://www.scipy.org/}),
          \package{matplotlib} (\url{https://matplotlib.org/})
          \package{Cython}(\url{http://cython.org}),
          }

@@

\appendix
\section{List of Affiliated Packages}
